---
title: "OX-I/18 Bulb tests"
author: "Brett Longworth"
date: "March 29, 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Summary

Results from the OX-I/18A OX-I/18B bulb tests. Data are examined as raw ratios
(with online d13C correction applied), and as normalized using snicser with
OX-I/15 as the normalizing standard. Data are not blank corrected, but this
should not affect the results. Summary plots and relevant summary data are
below.


## Setup

```{r, warning=FALSE, message=FALSE}
library(broom)
library(knitr)
library(dplyr)
library(ggplot2)
library(amstools)

options(digits = 5)

#define CI
ci <- function(x) 1.96 * sqrt((var(x)/length(x)))
```


## Read the data...

```{r}
# load usams
usams <- getWheel("USAMS032818") %>%
  filter(wheel_pos < 42,
         !grepl("Standard", sample_name)) %>%
  mutate(run = "USAMSA")
# load cfams
cfams <- getWheel("CFAMS032718") %>% 
  filter(wheel_pos > 88) %>%
  mutate(run = "CFAMS")

# second usams
usamsb <- read.delim("/mnt/shared/USAMS/Results/USAMS032818_TargetTable.xls") %>%
  filter(Pos < 42,
         !grepl("Standard", SampleName),
         !grepl("OX-II", SampleName)) %>%
  mutate(run = "USAMSB")
  
#Combine runs
data <- rbind(usams, cfams)

#Just look at OX-I
data <- data %>% 
  filter(!grepl("OX-II", sample_name)) %>%
  mutate(system = substr(wheel, 0, 5))

# Read the raw data...
# load usams
usamsr <- getRawWheel("USAMS032818") %>%
  filter(wheel_pos < 42,
         !grepl("Standard", sample_name))
# load cfams
cfamsr <- getRawWheel("CFAMS032718") %>% 
  filter(wheel_pos > 88)

#Combine runs
rdata <- rbind(usamsr, cfamsr)

#Just look at OX-I
rdata <- rdata %>% 
  filter(!grepl("OX-II", sample_name)) %>%
  mutate(system = substr(wheel, 0, 5))
```

## Summary plots

### CFAMS and USAMS data

```{r, echo=FALSE}
ggplot(data, aes(sample_name, fm_corr, color = system)) +
  geom_boxplot() +
  geom_hline(yintercept = 1.0398)
```

### USAMS second run

I took a second run of the USAMS samples to see if OXI/18B was repeatably a little high. It came back into line with the other gas samples in this run.

```{r, echo=FALSE}
ggplot(usamsb, aes(SampleName, NormRat)) +
  geom_boxplot() +
  geom_hline(yintercept = 1.0398)
```

### Raw data, online 13C corrected

Difference between systems is expected with unnormalized data.

```{r, echo=FALSE}
ggplot(rdata, aes(sample_name, corr_14_12, color = system)) +
  geom_boxplot() +
  theme(axis.text.x  = element_text(angle=90)) +
  facet_grid(. ~ system)
```

## Summary data

Data summarized by run. Fields are mean Fm (Fm.m), mean reported error (Fm.re),
sd of Fm (Fm.sd), and the low (CIL) and high (CIH) ends of the 95% confidence
interval on the mean.

```{r, echo=FALSE}
sum <- data %>% 
  select(sample_name, system, fm_corr, sig_fm_corr) %>% 
  group_by(system, sample_name) %>% 
  summarise("Mean Fm" = mean(fm_corr),
            "Mean RE" = mean(sig_fm_corr),
            "Std Dev" = sd(fm_corr),
            "95% CI" = paste(signif(mean(fm_corr) - ci(fm_corr), digits = 5), "-",
                             signif(mean(fm_corr) + ci(fm_corr), digits = 5)),
            N = n()
  )
kable(sum)
```


## Statistical tests

Analysis of Variance (ANOVA) should show us if groups show a significant difference in means. F-statistics under 3 and p-values greater than 0.005 indicate that we can
not reject the null hypothesis (groups are the same).

### An analysis of variance for each system separately...

```{r}
 aov <- data %>% 
   select(sample_name, system, fm_corr, sig_fm_corr) %>% 
   group_by(system) %>%
   do(tidy(aov(fm_corr ~ sample_name, data = .)))
 kable(aov)
```

### And together, using run and sample type as factors....

```{r}
data.aov <- aov(fm_corr ~ sample_name * system, data)
kable(tidy(data.aov))
```

### The same analysis with the raw data.

The increased p-statistic reflects the similarity in means among the raw data.

```{r}
datar.aov <- aov(corr_14_12 ~ sample_name, rdata)
kable(tidy(datar.aov))
```

For all analyses, we can accept the null hypothesis (means are the same) on pretty much any level.

### Summary data from the ANOVA...
```{r}
print(model.tables(data.aov,"means"),digits=5)
```

