---
title: "OX-I/20 Bulb tests"
author: "Brett Longworth"
date: "July 13, 2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Summary

Results from the OX-I/20 bulb tests. Data are examined as normalized ratios
(with online d13C correction applied), and as blank corrected data using snicser with
OX-I/18 as the normalizing standard. Summary plots and relevant summary data are
below.


## Setup

```{r, warning=FALSE, message=FALSE}
library(broom)
library(knitr)
library(dplyr)
library(stringr)
library(ggplot2)
library(amstools)
library(gt)

options(digits = 5)

#define CI
ci <- function(x) 1.96 * sqrt((var(x)/length(x)))

# wheels to examine
wheels <- c("CFAMS061720", "CFAMS071020")
```


## Read the data...

```{r}
# Function to get data
getBulbOx <- function(wheels) {
getWheel(wheels) %>% 
  filter(str_detect(sample_name, "^OX-?[I1][ \\/]") | 
         str_detect(sample_name, "^Oxalic Acid I ")) %>% 
  mutate(system = substr(wheel, 0, 5),
         name = recode(sample_name,
                      "OX-1/18 B UCI-1681B" = "OX-I/18B",
                      "Oxalic Acid I granules (SRM 4990 B HOxI)" = "OX-I Solid",
                      "OXI/20A UCI#1684A " = "OX-I/20A",
                      "OXI/20B UCI#1684B " = "OX-I/20B",
                      "OXI/20C UCI#1684AC" = "OX-I/20C"),
         Fm = ifelse(is.na(fm_mb_corr), fm_corr, fm_mb_corr),
         sig_Fm = ifelse(is.na(fm_mb_corr), sig_fm_corr, sig_fm_mb_corr),
         norm_err = pmax(int_err, ext_err)) %>% 
  group_by(sample_name, wheel) %>% 
    mutate(Rep = 1:length(Fm)) %>%
  ungroup()
  
}

data <- getBulbOx(wheels) 
```

# Normalized data

These data are normalized to OX-I/18B, but have no blank correction. Errors are the larger of the repeatablity or counting statistical error.

## Summary plots

```{r, echo=FALSE}
data %>% 
  ggplot(aes(name, norm_ratio, color = name, group = factor(Rep))) +
  geom_boxplot(aes(group = name), outlier.shape = NA) +
  geom_pointrange(aes(ymin = norm_ratio - norm_err,
                      ymax = norm_ratio + norm_err), 
                position=position_dodge(width = .5)) +
  scale_color_viridis_d() +
  geom_hline(yintercept = 1.0398) +
  labs(title = "OX-I on CFAMS061720 and CFAMS071020",
       subtitle = "OX-I/18B used as normalizing standard",
       x = NULL) +
  theme_classic() +
  facet_grid(rows = vars(wheel))
```

## Summary data

Data summarized by run. Fields are mean Fm (Fm.m), mean reported error (Fm.re),
sd of Fm (Fm.sd), and the low (CIL) and high (CIH) ends of the 95% confidence
interval on the mean.

```{r, echo=FALSE, message=FALSE}
data %>% 
  select(wheel, name, "Fm" = norm_ratio, "sig_Fm" = norm_err) %>% 
  group_by(wheel, name) %>% 
  summarise("Mean Fm" = mean(Fm),
            "Mean RE" = mean(sig_Fm),
            "Std Dev" = sd(Fm),
            "95% CI" = paste(signif(mean(Fm) - ci(Fm), digits = 5), "-",
                             signif(mean(Fm) + ci(Fm), digits = 5)),
            N = n()
  ) %>% 
  gt %>% 
  tab_header(title = "Summary data per wheel for normalized OX-I",
             subtitle = "No blank correction") %>% 
  fmt_number(columns = c(3:5), decimals = 4)
```


## Statistical tests

Analysis of Variance (ANOVA) should show us if groups show a significant difference in means. F-statistics under 3 and p-values greater than 0.005 indicate that we can
not reject the null hypothesis (groups are the same).


```{r}
 data %>% 
  select(wheel, name, "Fm" = norm_ratio, "sig_Fm" = norm_err) %>% 
  group_by(wheel) %>% 
  do(tidy(aov(Fm ~ name, data = .))) %>% 
  gt
```

# Blank corrected data

Blank correction should be very small and add little error for GS samples. OC samples (solid OX-I) will see a positive correction and slightly increased error.

## Summary plots

```{r, echo=FALSE}
data %>% 
ggplot(aes(name, Fm, color = name, group = factor(Rep))) +
  geom_boxplot(aes(group = name), outlier.shape = NA) +
  geom_pointrange(aes(ymin = Fm - sig_Fm, ymax = Fm + sig_Fm), 
                position=position_dodge(width = .5)) +
  scale_color_viridis_d() +
  geom_hline(yintercept = 1.0398) +
  labs(title = "OX-I on CFAMS061720 and CFAMS061020",
       subtitle = "OX-I/18B used as normalizing standard, Blank correction applied",
       x = NULL) +
  theme_classic() +
  facet_grid(rows = vars(wheel))
```

## Summary data

Data summarized by run. Fields are mean Fm (Fm.m), mean reported error (Fm.re),
sd of Fm (Fm.sd), and the low (CIL) and high (CIH) ends of the 95% confidence
interval on the mean.

```{r, echo=FALSE, message=FALSE}
data %>% 
  select(wheel, name, Fm, sig_Fm) %>% 
  group_by(wheel, name) %>% 
  summarise("Mean Fm" = mean(Fm),
            "Mean RE" = mean(sig_Fm),
            "Std Dev" = sd(Fm),
            "95% CI" = paste(signif(mean(Fm) - ci(Fm), digits = 5), "-",
                             signif(mean(Fm) + ci(Fm), digits = 5)),
            N = n()
  ) %>% 
  gt %>% 
  tab_header(title = "Summary data per wheel for normalized OX-I",
             subtitle = "Blank correction applied") %>% 
  fmt_number(columns = c(3:5), decimals = 4)
```


## Statistical tests

Analysis of Variance (ANOVA) should show us if groups show a significant difference in means. F-statistics under 3 and p-values greater than 0.005 indicate that we can
not reject the null hypothesis (groups are the same).


```{r}
 data %>% 
   select(wheel, name, Fm, sig_Fm) %>% 
  group_by(wheel) %>% 
   do(tidy(aov(Fm ~ name, data = .))) %>% 
  gt
```

