---
title: "AnalyseOX15"
author: "Brett Longworth"
date: "1/16/2016"
output:
  html_document:
    df_print: paged
---

# Summary

Results from the OX-I/15A OX-I/15B bulb tests. The data are normalized using
snicser with OX-I/13B as the normalizing standard. Data are not blank
corrected, but this should not affect the results. The wheel was run twice, and
the second run is clearly the better of the two. Both runs indicate that all
three OX's are the same within error. Summary plots and relevant summary data
are below.


## Setup

```{r, warning=FALSE, message=FALSE}
library(broom)
library(knitr)
library(dplyr)
library(ggplot2)

options(digits = 5)

#define CI
ci <- function(x) 1.96 * sqrt((var(x)/length(x)))
```


## Read the data...

```{r}
#Load both runs
dataa <- read.delim("USAMS011316_TargetTable.xls")
dataa$run <- "USAMSA"
datab <- read.delim("USAMS011316B_TargetTable.xls")
datab$run <- "USAMSB"

# load cfams
datac  <- read.delim("CFAMS101215_TargetTable.xls")
datac$run <- "CFAMS"

#Combine runs
data <- rbind(dataa, datab, datac)

#Just look at OX-I
data <- data %>% filter(Pos < 37,
                        grepl("OX-I", SampleName), 
                  			!grepl("OX-II", SampleName))
```

## Summary plots

```{r, echo=FALSE}
ggplot(data, aes(SampleName, NormRat)) +
  geom_boxplot() + 
  facet_grid(. ~ run)
```

## Summary data

Data summarized by run. Fields are mean Fm (Fm.m), mean reported error (Fm.re),
sd of Fm (Fm.sd), and the low (CIL) and high (CIH) ends of the 95% confidence
interval on the mean.

```{r, echo=FALSE}
sum <- data %>% 
  select(SampleName, run, NormRat, IntErr, ExtErr) %>% 
  mutate(merr = pmax(IntErr, ExtErr)) %>% 
  group_by(run, SampleName) %>% 
  summarise("Mean Fm" = mean(NormRat),
            "Mean RE" = mean(merr),
            "Std Dev" = sd(NormRat),
            "95% CI" = paste(signif(mean(NormRat) - ci(NormRat), digits = 5), "-",
                             signif(mean(NormRat) + ci(NormRat), digits = 5)),
            N = n()
  )
kable(sum)
```

Using data from CFAMS and the better USAMS run, pooled:

```{r, echo=FALSE}
sum <- data %>% 
  filter(run != "USAMSA") %>%
  select(SampleName, run, NormRat, IntErr, ExtErr) %>% 
  mutate(merr = pmax(IntErr, ExtErr)) %>% 
  group_by(SampleName) %>% 
  summarise("Mean Fm" = mean(NormRat),
            "Mean RE" = mean(merr),
            "Std Dev" = sd(NormRat),
            "95% CI" = paste(signif(mean(NormRat) - ci(NormRat), digits = 5), "-",
                             signif(mean(NormRat) + ci(NormRat), digits = 5)),
            N = n()
  )
kable(sum)
```


## Statistical tests

TODO: describe statistical tests.

### An analysis of variance for each run separately...

```{r}
 aov <- data %>% 
   select(SampleName, run, NormRat, IntErr, ExtErr) %>% 
   mutate(merr = max(IntErr, ExtErr)) %>% 
   group_by(run) %>%
   do(tidy(aov(NormRat ~ SampleName, data = .)))
 kable(aov)
```

### And together, using run and sample type as factors....

```{r}
data.aov <- aov(NormRat ~ SampleName * run, data)
kable(tidy(data.aov))
```

For both analyses, we can accept the null hypothesis (means are the same) on pretty much any level.

### Summary data from the ANOVA...
```{r}
print(model.tables(data.aov,"means"),digits=5)
```

