---
title: "OX-I/20 Bulb tests"
author: "Brett Longworth"
date: "June 23, 2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Summary

Results from the OX-I/20 bulb tests. Data are examined as raw ratios
(with online d13C correction applied), and as normalized using snicser with
OX-I/18 as the normalizing standard. Data are not blank corrected, but this
should not affect the results. Summary plots and relevant summary data are
below.


## Setup

```{r, warning=FALSE, message=FALSE}
library(broom)
library(knitr)
library(dplyr)
library(ggplot2)
library(amstools)

options(digits = 5)

#define CI
ci <- function(x) 1.96 * sqrt((var(x)/length(x)))
```


## Read the data...

```{r}
# load cfams
data <- getWheel("CFAMS061720") %>% 
  filter(grepl("O[xX]", sample_name),
         wheel_pos != 84) %>%
  mutate(system = substr(wheel, 0, 5),
         name = recode(sample_name,
                      "OX-1/18 B UCI-1681B" = "OX-I/18B",
                      "Oxalic Acid I granules (SRM 4990 B HOxI)" = "OX-I Solid",
                      "OXI/20B UCI#1684B " = "OX-I/20B",
                      "OXI/20C UCI#1684AC" = "OX-I/20C"),
         Fm = ifelse(is.na(fm_mb_corr), fm_corr, fm_mb_corr),
         sig_Fm = ifelse(is.na(fm_mb_corr), sig_fm_corr, sig_fm_mb_corr)) %>% 
  group_by(sample_name) %>% 
    mutate(Rep = 1:length(Fm)) %>%
  ungroup()
```

## Summary plots

### CFAMS and USAMS data

```{r, echo=FALSE}
data %>% 
ggplot(aes(name, Fm, color = name, group = factor(Rep))) +
  geom_pointrange(aes(ymin = Fm - sig_Fm, ymax = Fm + sig_Fm), 
                position=position_dodge(width = .5)) +
  scale_color_viridis_d() +
  geom_hline(yintercept = 1.0398) +
  labs(title = "OX-I on CFAMS061720",
       subtitle = "OX-I/18B used as normalizing standard",
       x = NULL) +
  theme_classic()
```

## Summary data

Data summarized by run. Fields are mean Fm (Fm.m), mean reported error (Fm.re),
sd of Fm (Fm.sd), and the low (CIL) and high (CIH) ends of the 95% confidence
interval on the mean.

```{r, echo=FALSE, message=FALSE}
data %>% 
  select(name, Fm, sig_Fm) %>% 
  group_by(name) %>% 
  summarise("Mean Fm" = mean(Fm),
            "Mean RE" = mean(sig_Fm),
            "Std Dev" = sd(Fm),
            "95% CI" = paste(signif(mean(Fm) - ci(Fm), digits = 5), "-",
                             signif(mean(Fm) + ci(Fm), digits = 5)),
            N = n()
  )
```


## Statistical tests

Analysis of Variance (ANOVA) should show us if groups show a significant difference in means. F-statistics under 3 and p-values greater than 0.005 indicate that we can
not reject the null hypothesis (groups are the same).

Note that although the groups don't look different, this isn't really enough data to do this reliably.

```{r}
 data %>% 
   select(name, Fm, sig_Fm) %>% 
   do(tidy(aov(Fm ~ name, data = .)))
```

