---
title: "AnalyseOX15"
author: "Brett Longworth"
date: "1/16/2016"
output: pdf_document
---

# Summary

Results from the OX-I/15A OX-I/15B bulb tests. The normalizing standard is OX-I/13B. Data are not blank corrected, but this should not affect the results. The wheel was run twice, and the second run is clearly the better of the two. Both runs indicate that all three OX's are the same within error. Summary plots and relevant summary data are below.

## Read the data...

```{r, warning=FALSE, message=FALSE}
library(broom)
library(knitr)
library(dplyr)
library(ggplot2)

options(digits = 5)

#define CI

ci <- function(x) 1.96 * sqrt((var(x)/length(x)))

#Load both runs
dataa <- read.delim("USAMS011316_TargetTable.xls")
dataa$run <- "USAMSA"
datab <- read.delim("USAMS011316B_TargetTable.xls")
datab$run <- "USAMSB"

# load cfams
datac  <- read.delim("CFAMS101215_TargetTable.xls")
datac$run <- "CFAMS"

#Combine runs
data <- rbind(dataa, datab, datac)

#Just look at OX-I
data <- data %>% filter(Pos < 37,
                        grepl("OX-I", SampleName), 
                  			!grepl("OX-II", SampleName))
```

## Summary plots

```{r, echo=FALSE}
ggplot(data, aes(SampleName, NormRat)) + geom_boxplot() + facet_grid(. ~ run)

```

## Summary data

Data summarized by run. Fields are mean Fm (Fm.m), mean reported error (Fm.re), sd of Fm (Fm.sd), and the low (CIL) and high (CIH) ends of the 95% confidence interval on the mean.

```{r, echo=FALSE}
sum <- data %>% 
  select(SampleName, run, NormRat, IntErr, ExtErr) %>% 
  mutate(merr = pmax(IntErr, ExtErr)) %>% 
  group_by(run, SampleName) %>% 
  summarise(Fm.m = mean(NormRat),
            Fm.re = mean(merr),
            Fm.sd = sd(NormRat),
            CIL = mean(NormRat) - ci(NormRat), 
            CIH = mean(NormRat) + ci(NormRat) 
            )
kable(sum)
```

Using data from CFAMS and the better USAMS run, pooled:

```{r, echo=FALSE}
sum <- data %>% 
  filter(run != "USAMSA") %>%
  select(SampleName, run, NormRat, IntErr, ExtErr) %>% 
  mutate(merr = pmax(IntErr, ExtErr)) %>% 
  group_by(SampleName) %>% 
  summarise(Fm.m = mean(NormRat),
            Fm.re = mean(merr),
            Fm.sd = sd(NormRat),
            CIL = mean(NormRat) - ci(NormRat), 
            CIH = mean(NormRat) + ci(NormRat) 
            )
kable(sum)
```


## Statistical tests


### An analysis of variance for each run separately...

```{r}
 aov <- data %>% 
   select(SampleName, run, NormRat, IntErr, ExtErr) %>% 
   mutate(merr = max(IntErr, ExtErr)) %>% 
   group_by(run) %>%
   do(tidy(aov(NormRat ~ SampleName, data = .)))
 kable(aov)
```

### And together, using run and sample type as factors....

```{r}
data.aov <- aov(NormRat ~ SampleName * run, data)
kable(tidy(data.aov))
```

For both analyses, we can accept the null hypothesis (means are the same) on pretty much any level.

### Summary data from the ANOVA...
```{r}
print(model.tables(data.aov,"means"),digits=5)
```

