---
title: "Caltech plots"
output:
  html_document:
    df_print: paged
---

Create a dataset. Add an index of replicates

```{r}
library(tidyverse)
data <- tribble(~val, ~ err, ~fact,
        1.1, .1, "A",
        1.0, .2, "A",
        1.2, .1, "A",
        2, .1, "B",
        1.9, .2, "B",
        2, .1, "B") 
```

Plotting by a factor gives us a bunch of overlapping points. Not good.

```{r}
ggplot(data, aes(fact, val)) +
  geom_errorbar(aes(ymin = val - err, ymax = val + err), width = 0.1) +
  geom_point()
```

In order to use position_dodge, we need to give it something to dodge by. `rep` is an index of replicates within the factor.

```{r}
data <- data %>% 
  group_by(fact) %>% 
  mutate(rep = 1:length(val)) %>% 
  ungroup
```

Now we can dodge the points by rep. We could label by rep, but if they're the same, this doesn't add anything. `group` adds `rep` as the group that `position_dodge` needs without changing the look of the points or lines.

```{r}
ggplot(data, aes(fact, val, group = rep)) +
  geom_errorbar(aes(ymin = val - err, ymax = val + err), width = 0.1, position=position_dodge(width = .5)) +
  geom_point(position=position_dodge(width = .5))
```

The same, but prettied up, and using geom_pointrange for value and error.

```{r}
ggplot(data, aes(fact, 
                 val, 
                 color = fact, 
                 ymin = val - err, 
                 ymax = val + err, 
                 group = rep)) +
  geom_pointrange(position=position_dodge(width = .5)) +
  scale_color_viridis_d() +
  labs(title = "Values and errors by fact",
       x = NULL) +
  theme_classic()
```

